### 2020-05-22 serial_guide.tex
diff

% Created by tikzDevice version 0.12.3 on 2020-05-05 20:39:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_0$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_1$};

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,535.89) -- (604.41,535.89);

\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,532.28) --
	(604.41,535.89) --
	(598.15,539.50);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_0$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_0+\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_0+\sigma+x_1$};

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,343.17) -- (604.41,343.17);

\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,339.56) --
	(604.41,343.17) --
	(598.15,346.78);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_1-\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_1-\sigma+x_0$};

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41,150.45) -- (282.16,150.45);

\path[draw=drawColor,line width= 1.1pt,line join=round] (288.42,154.06) --
	(282.16,150.45) --
	(288.42,146.84);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-22 09:42:54
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_1$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_2$};

@@

\path[draw=drawColor,line width= 1.7pt,line join=round] (282.16,535.89) -- (604.41,535.89);

\path[draw=drawColor,line width= 1.7pt,line join=round] (598.15,532.28) --
	(604.41,535.89) --
	(598.15,539.50);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_1$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_1+\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_1+\sigma+x_2$};

@@

\path[draw=drawColor,line width= 1.7pt,line join=round] (282.16,343.17) -- (604.41,343.17);

\path[draw=drawColor,line width= 1.7pt,line join=round] (598.15,339.56) --
	(604.41,343.17) --
	(598.15,346.78);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_2-\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_2-\sigma+x_1$};

@@

\path[draw=drawColor,line width= 1.7pt,line join=round] (604.41,150.45) -- (282.16,150.45);

\path[draw=drawColor,line width= 1.7pt,line join=round] (288.42,154.06) --
	(282.16,150.45) --
	(288.42,146.84);
